---
title: "PSTAT 5LS Spring 2023"
author: "Your Name Here"
date: "Week of April 10, 2023"
output: pdf_document
---

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Code

Use the chunks below to try out any code that you'd like. We have loaded the `penguins` data set for you in the first chunk, so you can try things out with this data.

```{r loadPenguins, error = T}
penguins <- read.csv("penguins.csv")
```

```{r tryIt1, error = T}
# Use this code chunk to print the phrase "Hello World!" to the screen

```

```{r tryIt2, error = T}
# Use this code chunk to compute what 5 times 7 is

```

```{r tryIt3, error = T}
# Use this code chunk to compute what 36 divided by 6 is, and assign it to x

```

```{r tryIt4, error = T}
# Use this code chunk to see what the value of x is by adding a line of code after x <- 6
x <- 6
```

```{r tryIt5, error = T}
# Use this code chunk to see what happens if you use X (capitalized) instead
X
```

```{r tryIt6, error = T}
# Use this code chunk to peek at the penguins data set

```

# Code Cheat Sheet

## `<-`
- Assigns a value to a name
- `name <- value`

## `read.csv(file, stringsAsFactors = TRUE)`
- `file` is the name of the file from which data are to be read
- `stringsAsFactors` should generally be set to `TRUE` (all caps): this determines how text-like data in a CSV file is interpreted by R.

## `head(x, n)`
- `x` is a data.frame
- `n` is the number of rows to print

## `str(object)`
- `object` is the R object about which you want to have some information (i.e., see the `str`ucture of).

