---
title: "PSTAT 5LS Lab 2 Report"
author: "YOUR NAME GOES HERE - KEEP THE QUOTES"
date: "TODAY'S DATE GOES HERE - KEEP THE QUOTES"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The data set `tuition_sample.csv` contains information about yearly cost of attendance, yearly cost of room and board, and yearly total cost of attendance (tuition + room and board) for 300 sampled public and private colleges and universities around the United States. 

In this lab, you will produce numerical and graphical displays to help you answer questions about the differences in tuition between private and public colleges.

**Collaborators:** If applicable, replace this text with the names of anyone you collaborated with on this project.

# Lab Assignment

## Question 0

In the chunk below, import ("read in") the data in `tuition_sample.csv` and call it `tuition`. Don't forget the `stringsAsFactors` argument. Hint: We read in the penguins data in the lab tutorial.

```{r question0, error = T}
# Use this code chunk to write the code necessary to answer the question. Do not start your code on this line, and do not start your code with # (this is a comment, R will ignore it).


```

## Question 1

a.  Create a histogram of in-state tuition for the colleges in the sample. Be sure to add a title and labels for the axes. Also provide the arguments `main`, `xlab`, and `ylab` for a plot title, x-axis label, and y-axis label.
b.  Create a histogram of out-of-state tuition for the colleges in the sample. Be sure to add a title and labels for the axes. Also provide the arguments `main`, `xlab`, and `ylab` for a plot title, x-axis label, and y-axis label.

```{r question1, error = T}
# Use this code chunk to write the code necessary to answer the question. Do not start your code on this line, and do not start your code with # (this is a comment, R will ignore it).
hist(tuition$in_state_tuition, 
     main = "Histogram of In-state Tuitions", 
     xlab = "In-state Tuition ($)", 
     ylab = "Number of Colleges")
hist(tuition$out_of_state_tuition, 
     main = "Histogram of Out-of-state Tuitions", 
     xlab = "Out-of-state Tuition ($)", 
     ylab = "Number of Colleges")

```

## Question 2

a.  Find and report the appropriate measure of center for in-state tuition from this data set.\
b.  Find and report the appropriate measure of center for out-of-state tuition from this data set.
c.  Are these values parameters or statistics?

Use the code chunk below to run the code you need. Then answer the questions after the code chunk.

```{r question2, error = T}
# Use this code chunk to write the code necessary to answer the question. Do not start your code on this line, and do not start your code with # (this is a comment, R will ignore it).









```

Replace this text with your answers to Question 2. 

## Question 3

Make a side-by-side boxplot of the quantitative variable in-state tuition by the categorical variable institution type.

```{r question3, error = T}
# Use this code chunk to write the code necessary to answer the question. Do not start your code on this line, and do not start your code with # (this is a comment, R will ignore it).





```

## Question 4

Make a side-by-side boxplot of the quantitative variable out-of-state tuition by the categorical variable institution type.

```{r question4, error = T}
# Use this code chunk to write the code necessary to answer the question. Do not start your code on this line, and do not start your code with # (this is a comment, R will ignore it).





```

## Question 5

Run the following code chunk so that you can see the summary statistics for in-state and out-of-state tuitions by type of institution.

```{r}
#Remove the # at the beginning of each of the code lines so that this function runs on the data
#tapply(tuition$in_state_tuition, tuition$type, summary)

#tapply(tuition$out_of_state_tuition, tuition$type, summary)

```

Does it appear that institution type (private, public) has an effect on in-state tuitions? On out-of-state tuitions? Be sure to address aspects of what you see in the side-by-side boxplots from Questions 3 and 4 and to the output from the code chunk above to support your answers.

# Answer
Replace this text with your answer to Question 5.

